Equipo 7

### 2021-05-09 final/avance/script.Rmd
Update script.Rmd

data1<-filter(data,pobtot<2500)

@@

#ahora triangular.
out = rdrobust(cambio_esp_top, cambio_internet, kernel = "triangular", p = 1, c=20,h = 5)
summary(out)

@@

out = rdbwselect(cambio_esp_top, cambio_internet, kernel = "triangular", p = 1, bwselect = "mserd")
summary(out)

@@

out = rdbwselect(cambio_esp_top, cambio_internet,c=20, kernel = "triangular", p = 1, bwselect = "mserd")
summary(out)

@@

>>>>

data1<-filter(data,pobtot<2500)
attach(data1)

@@

#ahora triangular.
out = rdrobust(cambio_esp_top, cambio_internet, kernel = "triangular", p = 4, c=20,h = 5)
summary(out)

@@

out = rdbwselect(cambio_esp_top, cambio_internet, kernel = "triangular", p = 4, bwselect = "mserd")
summary(out)

@@

out = rdbwselect(cambio_esp_top, cambio_internet,c=20, kernel = "triangular", p = 4, bwselect = "mserd")
summary(out)

@@

# ahora lo incorporamos

out = rdrobust(cambio_esp_top, cambio_internet,c=20, kernel = "triangular", p = 4, bwselect = "mserd")
